Manuscript

### 2014-10-13 inst/simulation/manuscript.Rmd
...

```{r figure-4-init}
getPopulationCorrelations <- function(modelName) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  populationCorrelations <- validation$getValidationSpatialPopulationSizes(modelNames=modelName)
  return(populationCorrelations)
}

@@

```{r figure-4abc}
pc1 <- getPopulationCorrelations(scenarios=scenarios, modelName=modelNames[1])
pc2 <- getPopulationCorrelations(scenarios=paste0(scenarios, "combined"), modelName=modelNames[1])
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelName=modelNames[1])

p1 <- plotPopulationCorrelations(p1)
saveFigure(p1, "manuscript-figure-4a.png", width=4, height=4)
plotPopulationCorrelations(p2)
p2 <- saveFigure(p2, "manuscript-figure-4b.png", width=4, height=4)
plotPopulationCorrelations(p3)
p3 <- saveFigure(p3, "manuscript-figure-4c.png", width=4, height=4)
```

>>>>

```{r figure-4-init}
getPopulationCorrelations <- function(scenarios, modelNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=scenarios, modelNames=modelNames)
  return(populationCorrelations)
}

@@

```{r figure-4abc}
pc1 <- getPopulationCorrelations(scenarios=scenarios, modelNames=modelNames[1])
pc2 <- getPopulationCorrelations(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1])
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1])

p1 <- plotPopulationCorrelations(p1)
saveFigure(p1, "manuscript-figure-4a.png", width=4, height=4)
p2 <- plotPopulationCorrelations(p2)
saveFigure(p2, "manuscript-figure-4b.png", width=4, height=4)
p3 <- plotPopulationCorrelations(p3)
saveFigure(p3, "manuscript-figure-4c.png", width=4, height=4)
```

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  return(credibilityIntervals)  
}

plotCIProportions <- function(credibilityIntervals) {
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI")
  return(p)
}
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)

p1 <- plotCIProportions(cip1)
saveFigure(p1, "manuscript-figure-5a.png", width=4, height=2)
p2 <- plotCIProportions(cip2)
saveFigure(p2, "manuscript-figure-5b.png", width=4, height=2)
p3 <- plotCIProportions(cip3)
saveFigure(p3, "manuscript-figure-5c.png", width=4, height=2)

```
